Atomify - a live LAMMPS visualizer

### 2016-10-10 ms.tex
Future work notes

Atomify solves this problem by combining the script editing, simulating and visualization into one single application. It uses LAMMPS as a library and executes commands one by one. A synchronization step copies the relevant information from LAMMPS to the GPU for visualization and data plotting.

@@

@@

\subsection{Future work}
Atomify is far from finished. 
A web version of Atomify is in development. 
All parts of Atomify can easily be ported to the web using WebGL and Emscripten.

>>>>

Atomify solves this problem by combining the script editing, simulating and visualization into one single application. It uses LAMMPS as a library and executes commands one by one. A synchronization step copies the relevant information from LAMMPS to the GPU for visualization and data plotting. The visualization is done using raytracing on billboards allowing rendering of millions of atoms with good framerate.

@@

\subsection{Script editor}
\subsection{Visualization}
\subsection{Live plotting}

@@

\subsection{Future work}
Atomify is far from finished.\\
A web version of Atomify is in development using WebGL and Emscripten. \\
Geometry shaders \\
Improved script editor with auto completion \\
Moltemplate interface \\
